DOpElib:\\ Differential Equations and Optimization Environment

### 2014-01-23 Examples/PDE/InstatPDE/Example3/content.tex
1) Sehr verwirrende (und falsche) Materialparameter in plasticity aufgeraeumt, 2) Typos in Doku beseitigt, da nicht mehr kompiliert (only_recent -> only\underline{}recent

This behavior is particularly useful, if many time steps are taken; so that the 
whole set of unknowns can no longer be stored in main memory. Note that all vectors 
will allocate the required memory when the vector is reinitialized to a new size.
Hence, for large vectors this may need some time.

To avoid multiple programs accessing the same files on the hard drive, a 
\texttt{lock} file is initialized. Under normal conditions, this will be deleted 
once the program terminates. However, should the program exit exceptionally, the 
lock file will still exist. Calling the program in this case will produce an 
exception, with the following text:
\begin{verbatim}
Warning: During execution of `StateVector<VECTOR>::StateVector` 
         the following Problem occurred!
The directory Results/tmp_state/ is propaply already in use.
\end{verbatim}
To resolve the issue, you have to delete the named directory with the 
temporary storage files manually.

>>>>

This behavior is particularly useful, if many time steps are taken; so that the 
whole set of unknowns can no longer be stored in main memory, but access to all
parts of the solution is required after the solution process and thus the 
option \texttt{only\underline{ }recent} used in Example~\ref{PDE_Instat_FSI} is not sufficient.
Note that all vectors 
will allocate the required memory when the vector is reinitialized to a new size.
Hence, for large vectors this may need some time.

To avoid multiple programs accessing the same files on the hard drive, a 
\texttt{lock} file is initialized. Under normal conditions, this will be deleted 
once the program terminates. However, should the program exit exceptionally, the 
lock file will still exist. Calling the program in this case will produce an 
exception, with the following text:
\begin{verbatim}
Warning: During execution of `StateVector<VECTOR>::StateVector` 
         the following Problem occurred!
The directory Results/tmp_state/ is probably already in use.
\end{verbatim}
To resolve the issue, you have to delete the named directory with the 
temporary storage files manually.
